%ACKNOWLEDGEMENTS page. 
%This page is optional

\clearpage
\begin{center}

\vspace*{5\baselineskip}
\textbf{\large Acknowledgements}
\end{center}

I have been so incredibly lucky to have been helped by many amazing mentors and colleagues during my time at Columbia.
In particular, my advisor Kathy McKeown took a chance on me and gave me many more years than I deserved to explore and learn, for which I am eternally grateful.
Fernando Diaz has also been a great intern advisor, mentor, musical collaborator, and someone who talked me off many a proverbial ledge.   
Sasha Rush, who was my TA in NLP, has been an amazing friend and mentor as well, giving me encouragement and advice throughout my entire time at Columbia.
Hal Daum{\'e} was always more generous with his time and advice than he needed to be.
Umut {\"O}zertem was a great intern advisor and kept looking out for me even after the summer had passed.

I'd also like to acknowledge my friends in the NLP lab, department, and various reading groups for all the discussions we have had over the years 
(my apologies if I forgot anyone): 
Emily Allaway,
Or Biran, 
Tuhin Chakrabarty, 
Chad DeChant,
Tom Effland, 
Katy Gero, 
Chris Hidey,
Jeff Jacobs,
Giannis Karamanolakis,
Faisal Ladhak,
Fei-Tzin Lee,
Wei-Yun Ma,
Jessica Ouyang,
Yves Petinot,
Jonathan Reeve,
Sara Rosenthal,
Victor Soto, 
Karl Stratos,
Kapil Thadani,
and
Elsbeth Turcan.

Finally, I'd like to acknowledge my wife, Alix, who has been unwavering in her support of this journey, and more than anyone has uplifted  me through the lows and celebrated the highs.


\begin{flushleft}
\hspace{10mm}
\end{flushleft}
\clearpage

%\pagenumbering{gobble}  %remove page number on summary page


